Data Preparation

### 2019-01-11 Data Preparation.Rmd
text #Selecting Variables

Our dataframe contains many variables that are either empty or meaningless for our analysis, thus we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.

```{r}
d_transcript <- d_transcript %>%
  filter(`Appraisal (Description)` == "Grade supervisor")
  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
         `Program (Description)`, `Academic Year`, `Academic Session`,
         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
  distinct %>%
  rename(`Student ID Number` = `Student Number`,
         `Course Code` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         `Civil Year` = `Academic Year`, # double check
         `Period` = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`,
         `Grade` = `Grade symbol`,
         `Status` = `Booking Status (Desc.)`) # is there a better name for the variable?
```

>>>>

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
d_transcript <- d_transcript %>%
  filter(`Appraisal (Description)` == "Grade supervisor")
  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
         `Program (Description)`, `Academic Year`, `Academic Session`,
         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
  distinct %>%
  rename(`Student ID Number` = `Student Number`,
         `Course Code` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         `Civil Year` = `Academic Year`, # double check
         `Period` = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`,
         `Grade` = `Grade symbol`,
         `Status` = `Booking Status (Desc.)`) # is there a better name for the variable?
```
